---
title: "Create list of users"
output: html_notebook
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidygraph)
library(rtweet)
library(ggraph)
library(stringr)
```

## 1. Get the list from camera dei deputati official twitter account (montecitorio)

```{r}
deputati <- lists_members("981119394062487552")
nrow(deputati)
```
## 2. Scrape the official site of the camera dei deputati for the names and group / party affiliations

This was done in python using the notebook "Web-scraping.ipynb" 
(Comment by Andreas: As part of another course this semester I had to scrape a website, therefore I used the opportunity to collect data about Italian politicians.)

```{r}
# read the file
list_deputati <- read.csv("deputati.csv", stringsAsFactors = F)
nrow(list_deputati)
```

## 3. Match the names of the two lists

Try to match twitter with official names

```{r}
#create an empty collumn for official names
#deputati
# loop over the list of official names
for (dep_name in list_deputati$name){
  # Get the surname
  patt = str_split(dep_name, " ")[[1]]
  # take care of special surnames
  if (patt[1] == "de" || patt[1] == "di" || patt[1] == "lo"  || patt[1] == "la"){
    patt = paste(patt[1], patt[2], sep = " ")
  } else {
    patt = toString(patt[1])
  }
  deputati$off_name[str_detect(deputati$name, regex(patt, ignore_case = T ) )] <- toString(list_deputati$name[str_detect(list_deputati$name, regex(patt, ignore_case = T ) )][1])
}
```

Perform manual cleaning

```{r}
deputati %>% 
  select(name, off_name) -> comparison_table
```

Remove official name for false matches

```{r}
false_matches<- c("Anna Bilotti", "Marco Rizzone", "Maria Marzana", "Andrea Giarrizzo", 
           "Antonio del Monaco", "UMBERTO DEL BASSO DE", "Federico Conte", 
           "stefania pezzopane", "guido della frera", "adelizzi cosimo", 
           "Marina Berlinghieri", "Elisa Tripodi", "Vito De Filippo", 
           "Graziano Delrio", "Raffaella Paita", "Diego Sozzani", "Raffaele Nevi",
           "Ugo Cappellacci", "amitrano alessandro", "Giorgio Mulè", 
           "CLAUDIO COMINARDI","Carlo Sibilia", "Federico D'Incà", 
           "Renata Polverini", "Mauro Del Barba", "Pier Luigi Bersani", 
           "Luigi Di Maio", "Simone Baldelli #iovotono", "Matteo Dall'Osso #iohovotatoNO"
           )

for (match in false_matches){
  deputati$off_name[deputati$name == match] <- ""
}
```

Manually change the pattern for screen names that have no matches 
see if the names agree:

```{r}
deputati %>% 
  select(name, off_name) %>% 
  filter(off_name == "")
```


```{r}
pattern = "Dall'osso"

list_deputati$name[str_detect(list_deputati$name, regex(pattern, ignore_case = T ) )]
deputati$name[str_detect(deputati$name, regex(pattern, ignore_case = T ) )]
```

If yes update the official name

```{r}
deputati$off_name[str_detect(deputati$name, regex(pattern, ignore_case = T ) )] <- toString(list_deputati$name[str_detect(list_deputati$name, regex(pattern, ignore_case = T ) )])
```

## 4. Search for not yet found members of the parliament trough the search users function

```{r}
all <- right_join(deputati, list_deputati, by = c("off_name" = "name") )
```

Generate a list of not yet found members of the parliament

```{r}
not_found <- all$off_name[is.na(all$name)]
```

Search Twitter for all the names in this list
and combine them in a not found dataframe

```{r}
for (name in not_found){
  nf_df <- rbind(nf_df, search_users(name))
}
```

Keep the users that write match the regular expression "deputat." in their description that is, those twitter useres that write about themselves that they are deputato/a

```{r}
nf <- nf_df[str_detect(nf_df$description, regex("deputat.", ignore_case = T ) ),]
```

As above match the surnames in the twitter user list with the official list

```{r}
nf$off_name = ""
for (dep_name in list_deputati$name){
      patt = str_split(dep_name, " ")[[1]]
    if (patt[1] == "de" || patt[1] == "di" || patt[1] == "lo"  || patt[1] == "la"){
      patt = paste(patt[1], patt[2], sep = " ")
    } else {
      patt = toString(patt[1])
    }
    nf$off_name[[str_detect(nf$name, regex(patt, ignore_case = T ) )]] <- toString(list_deputati$name[str_detect(list_deputati$name, regex(patt, ignore_case = T ) )][1])
}
```

Previse matching manually

```{r}
nf %>% 
  select(name, off_name, screen_name)
```

Perform an inner join with the official list

```{r}
nf %>% 
  inner_join(list_deputati, by = c("off_name" ="name")) -> nf
```

Selct the relevant columns

```{r}
nf %>% 
  select(user_id, name, screen_name, description, off_name, url.y, cessato, gruppo, url_gruppo, sub_gruppo, sub_gruppo_url) %>% 
  rbind(new) -> new
```

Collate both dataframes

```{r}
deputati %>% 
  select(user_id, name, screen_name, description, off_name, url.y, cessato, gruppo, url_gruppo, sub_gruppo, sub_gruppo_url) %>% 
  rbind(new) -> new

# Remove duplicates for sanity
unique(new) -> new
```

Check the list for politicians that dropped out

```{r}
new %>% 
  selct(cessato) %>% 
  filter(cessato != "False")
```

Manually remove politicians that abandoned their charge before the party split by changing the date in the cell below

```{r}
new %>% 
  filter(cessato != "2018-09-25 00:00:00") -> new
```

Safe the results

```{r}
saveRDS(new, "userlist.rds")
```

