---
title: "Create Networks"
output:
  pdf_document: default
  html_notebook: default
---

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidygraph)
library(rtweet)
library(ggraph)
library(stringr)
```

Combine all files into one dataframe and save it to timelines.rds

```{r read the data}
files <- list.files(path = "./timelines/")
for (file in files){
 df <- rbind(df, readRDS(paste("./timelines/", file, sep = "")))
}
saveRDS(df, file = "timelines.rds")
```

```{r}
df <- readRDS("timelines.rds")
```

# Whole Parliament
Read the list of users and filter the tweets that have been retweeted by users from within the userlist.

```{r construct the network}
user_df <- readRDS("userlist.rds")
ids <- as.data.frame(user_df$user_id)
names(ids) <- c("user_id")

df %>% 
  inner_join(ids, by = c("retweet_user_id" = "user_id")) %>% 
  filter(user_id != retweet_user_id) -> network
```

Construct the graph with weighted edges (by number of retweets)

```{r create the graph}
network %>% 
  inner_join(user_df) %>% 
  group_by(user_id, screen_name, gruppo) %>% 
  select(user_id, screen_name, gruppo) %>% 
  unique() -> vertices

network %>% 
  select(from = retweet_user_id, to = user_id) %>% 
  group_by(from, to) %>% 
  filter(from %in% vertices$user_id & to %in% vertices$user_id) %>% 
  summarise(weight = n()) -> edges

graph <- tbl_graph(vertices, edges, directed = F, node_key = "user_id")
```

```{r save the graph}
saveRDS(network, "retweet_network.rds")
saveRDS(vertices, "retweet_nw_vert.rds")
saveRDS(edges, "retweet_nw_edg.rds")
saveRDS(graph, "retweet_graph.rds")
```

# Split
Create the network of party-members of the parties of interest, only considering data befor the split occured.

```{r filter out PD and IV before the split}
user_df %>% 
  filter(gruppo == "ITALIA VIVA") -> user_df_split

user_df %>% 
  filter(gruppo == "PARTITO DEMOCRATICO") %>% 
  rbind(user_df_split) -> user_df_split

ids <- as.data.frame(user_df_split$user_id)
names(ids) <- c("user_id")

df %>% 
  inner_join(ids, by = c("retweet_user_id" = "user_id")) %>% 
  filter(user_id != retweet_user_id, created_at < "2019-09-18 00:00:00" ) -> network_split
```

```{r create graph before}
network_split %>% 
  inner_join(user_df_split) %>%
  group_by(user_id, screen_name, gruppo) %>% 
  select(user_id, screen_name, gruppo) %>% 
  unique() -> vertices_split

network_split %>% 
  select(from = retweet_user_id, to = user_id) %>% 
  group_by(from, to) %>% 
  filter(from %in% vertices_split$user_id & to %in% vertices_split$user_id) %>% 
  summarise(weight = n()) -> edges_split

graph_split <- tbl_graph(vertices_split, edges_split, directed = F, node_key = "user_id")
```

```{r save graph before}
saveRDS(network_split, "retweet_network_split.rds")
saveRDS(vertices_split, "retweet_nw_vert_split.rds")
saveRDS(edges_split, "retweet_nw_edg_split.rds")
saveRDS(graph_split, "retweet_graph_split.rds")
```

